Integrating brain and biomechanical models - a new paradigm for understanding neuro-muscular control

### 2018-01-12 papers/integration/omm_integ.tex
Addresses Reviewer 1 final comment

% Use colour to indicate changes made following review. Can be
% set to this 'black' colour prior to final publication:
\newcommand{\black}{\textcolor{black}}
% Colour for reviewer 1 changes:
\newcommand{\rvwcolour}{\textcolor{OrangeRed}}
% Colour for reviewer 2 changes:
\newcommand{\rvwcolourtwo}{\textcolor{Cerulean}}
% Commands to use in the text. Change 'rvwcolour/rvwcolourtwo' to
% 'black' to hide review changes.
\newcommand{\rvw}[1]{\rvwcolour{#1}}
\newcommand{\rvwt}[1]{\rvwcolourtwo{#1}}

@@

\tiny
 \keyFont{
   \section{Keywords:}
   integrated brain biomechanics neuromuscular oculomotor saccade basal ganglia
 } % 5 to 8 keywords
\end{abstract}

@@

% Remove after review:
\bol{Note:} Changes based on Reviewer 1's comments \rvw{are in this colour}. For
Reviewer 2 \rvwt{we use this colour}.

@@

\rvw{We have called this closed-loop, biomimetic modelling approach \e{computational
neurobehaviour}, in which a complete, behaving model is constructed,
with attention paid to the biological accuracy of each brain and
biomechanical sub-system. There already exist many
closed-loop \e{robotic} systems which receive sensory input from the
world, process that input and generate behaviour by activating motor
systems
\citep{yu_development_2004,fend_artificial_2004,pearson_whiskerbot:_2007}. We
now consider whether robotic systems which model biological
components \e{in hardware} could fall within our new category.
%
Using a number of examples, we will attempt to illustrate what we mean
by computational neurobehaviour. We'll consider which examples fall
into the new category and which are covered by other fields of
robotics or computational neuroscience.}

@@

\rvw{Modern programming platforms, often originating from the
computer game industry, make it relatively easy to model a virtual
environment. Consequently, an increasing number of studies into
robotic or neuromimetic control are carried out with virtual robots
operating within a virtual environment.}
%
\rvw{\cite{nguyen_saccade_2014} and
\cite{thurat_biomimetic_2015} are two studies of the oculomotor system
which model sensory input, neural control \e{and} motor output in
software. These studies fall outside the remit of computational
neurobehaviour only because they omit to close the sensory
loop. \cite{dewolf_spiking_2016} describes a reach model comprising a
simplified virtual arm (with fewer degrees of freedom than a primate
arm), and a biologically inspired brain model. This model also omits
to close the sensory feedback loop and we consider it a computational
neuroscience study of a (virtually) embodied model.}
%

>>>>

% Used colour to indicate changes made following review.
% These commands are now defined to be no-ops
\newcommand{\rvw}[1]{#1}  % Reviewer 1.
\newcommand{\rvwf}[1]{#1} % Reviewer 1, final comment
\newcommand{\rvwt}[1]{#1} % Reviwer 2.

@@

\tiny
 \keyFont{
   \section{Keywords:}
   integrated brain biomechanics neuromuscular neuromechanics oculomotor saccade basal-ganglia
 } % 5 to 8 keywords
\end{abstract}

@@

@@

\rvw{We have called this closed-loop, biomimetic modelling approach \e{computational
neurobehaviour}, in which a complete, behaving model is constructed,
with attention paid to the biological accuracy of each brain and
biomechanical sub-system.
% Address final comment from Reviewer 1
\rvwf{We are by no means the first researchers to consider this
interaction between brain and biomechanics. Integrative approaches to
motor control have been referred to as \e{neuromechanics} by some
authors~\citep{nishikawa_neuromechanics:_2007}. This field appears to
have developed from detailed and low level studies of the mechanics of
muscle control systems, focussing on the neural systems `closest' to
the muscle~\citep{chiel_brain_2009}. It is evident that a recognition
of the importance of sensory input to these systems has evolved within
this field. Indeed, \cite{edwards_neuromechanical_2010} specifically
reviews closed-loop, \e{neuromechanical simulations} of behaviour in
three organisms; fly, locust and cat. The term neuromechanical
simulation \citep{pearson_assessing_2006,edwards_neuromechanical_2010}
is analogous to our computational neurobehaviour, although it does not
emphasise the important \e{behavioural} aspect of the works.}

There also exist many
closed-loop \e{robotic} systems which receive sensory input from the
world, process that input and generate behaviour by activating motor
systems
\citep{yu_development_2004,fend_artificial_2004,pearson_whiskerbot:_2007}. We
now consider whether robotic systems which model biological
components \e{in hardware} could fall within our new category.
%
Using a number of examples, we will attempt to illustrate what we mean
by computational neurobehaviour. We'll consider which examples fall
into the new category and which are covered by other fields of
robotics or computational neuroscience.}

@@

\rvw{Modern programming platforms, often originating from the
computer game industry, make it relatively easy to model a virtual
environment. Consequently, an increasing number of studies into
robotic or neuromimetic control are carried out with virtual robots
operating within a virtual environment.}
%
\rvwf{This approach is taken in the studies described
in \cite{edwards_neuromechanical_2010}. \cite{dickson_integrative_2006}
describes an integrated model of Drosophila flight in which visual
input is processed by an algorithmic (that is, non-neural) `brain' to
control a biomechanically accurate representation of the fly. As the
virtual fly traverses its environment, its visual input updates,
closing the loop of the simulation. \cite{cope_model_2016} is a recent
study which omits the biomechanically accurate component of the model
but could provide the biologically plausible brain to make a
computational neurobehavioural fly
model. \cite{cofer_neuromechanical_2010} use an environment called
AnimatLab \citep{cofer_animatlab:_2010} to simulate the locust's
jumping mechanism in an open-loop, software-only investigation. As
this appears to be a feed-forward model without sensory feedback, we
would describe it as an input-assumption model.}
%
\rvw{\cite{nguyen_saccade_2014} and
\cite{thurat_biomimetic_2015} are two studies of the oculomotor system
which model sensory input, neural control \e{and} motor output in
software. These studies fall outside the remit of computational
neurobehaviour only because they omit to close the sensory
loop. \cite{dewolf_spiking_2016} describes a reach model comprising a
simplified virtual arm (with fewer degrees of freedom than a primate
arm), and a biologically inspired brain model. This model also omits
to close the sensory feedback loop and we consider it a computational
neuroscience study of a (virtually) embodied model.}
%
